---
title: "Price Data Analysis"
author: "Pankaj Kumar , Karl Jurek, Shawn Jung"
date: "5/31/2019"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stats)
library(broom)
price_modeling_data = read.csv('Data/modelingData.csv' )
```

## Introduction

   Using the Modeling.csv file we created the following models:
   
   
   Stepwise
   
   
   LASSO
   
   
   Final 
   
   
   to predict the cost of housing in the predictionData.csv file. 


## Data Description

   The modelingData.csv file contains properties sold between August 20, 2011 and June    30, 2015.
   
   
   25471 observations / rows
   
   
   292 variables / columns
   
   
   The predictionData.csv file contains properties sold between July 2015 and May2016.
   
   
   5000 observations / rows
   
   
   291 variables / columns


## Data Cleaning / Wrangling
   ** Initial import of the the modelingData.csv and predictionData.csv required stringsAsFactors=F 
   
   
   ** Converting Time Stamp from integer based to date format (yyyy-mm-dd)
   
   
   ** modeling_df=transform(modeling_df, timestamp=as.Date(timestamp, origin = "1899-12-30"))
   
   
   ** projection_df=transform(projection_df, timestamp=as.Date(timestamp, origin = "1899-12-30"))


### Build_year - 
   ** 14965 transformed to 1965
   
   
   ** 1691 transformed to 1991
   
   
   ** 20052009 transformed to 2007


### Kitch_sq
   ** 2013 deleted due to being the same as the build_year
   
   
   ** 2014 deleted due to being the same as the build_year
   
   
   ** 1974 deleted due to being the same as the build_year
   
   
   ** 1970 deleted due to being larger than the entire square footage of the building


### State
   33 transformed to 3


Removed all apostrophe / single quotes from sub_area


There are 
Deleted 7991 rows where the max_floor, material, build_year, num_room, kitch_sq, and state all had a value of NA.


Deleted 1791 rows where the life_sq, build_year, and state all had a value of NA.


Deleted 1038 rows where the life_sq and build_year had a value of NA.
Deleted 261 rows where the life_sq and state had a value of NA.
Deleted 232 rows where the build_year and state had a value of NA.



## EDA  

### Univariate Analysis 

```{r echo = FALSE}

na_count <-sapply(price_modeling_data, function(y) sum(length(which(is.na(y)))))
na_count_frame= stack(na_count)
all_na= filter(na_count_frame, na_count==25471)
no_na = filter(na_count_frame, na_count==0)

ggplot(data = filter(na_count_frame , values >10000))+
  geom_bar(mapping = aes(y= values, x=ind), stat='identity')+
  xlab('variable name')+
  ylab('number of NAs')+
  coord_flip();
```

### Bivariate Analysis 


```{r echo =F}

p = ggplot(data = price_modeling_data, aes(  y = price_doc))
# below should be used with geom_point
lm_smooth_line=stat_smooth(method = "lm", aes(  y = price_doc), col = "red")
p+geom_point(mapping = aes( x= life_sq)) +
   stat_smooth(method = "lm", aes( x= life_sq), col = "red")

  
# num_room looks like a categorical variable with around 15 values
p+geom_point(mapping = aes( x = num_room))

p+geom_bar(mapping = aes( x = num_room), stat = "identity") + 
  coord_flip()


# kitchen_sq
p+geom_point(mapping = aes( x= kitch_sq))+
     stat_smooth(method = "lm", aes( x= kitch_sq), col = "red")


p+geom_bar(mapping = aes( x = floor), stat = "identity") 
p+geom_bar(mapping = aes( x = max_floor), stat = "identity") 
p+geom_point(mapping = aes( x = build_year)) 
p+geom_bar(mapping = aes( x = build_year), stat = "identity") 
p+geom_bar(mapping = aes( x = sub_area), stat = "identity") + coord_flip()
p+geom_bar(mapping = aes( x = build_year), stat = "identity") 

print(p+geom_bar(mapping = aes( x = radiation_raion), stat = "identity") )

```

### Transformations 


```{r echo = F}


```

### Outliears 

 Outliers
 
 
Full_sq - 5326


```{r echo = F}
  pr_model = lm(price_doc ~ full_sq+work_all  , price_modeling_data)
cookd=cooks.distance(pr_model)
summary(pr_model)

df <- augment(pr_model)
ggplot(df, aes(x = .fitted, y = .resid)) + geom_point()

```
 

### Interaction Terms 




## Modeling
      OLS
      LASSO
      
      
## Final Prediction

